Analysing Constraint Grammars with a SAT solver

### 2015-10-23 paper/lrec/eval_futurework.tex
amount of variables per symbolic word

The Spanish grammar had an erroneous set definition, where a word was required to have almost all POS tags at the same time. After fixing the set definition, our test didn't reveal other problems.
The program marked \todo{n} problem rules for the Finnish grammar, but we didn't have time to verify if all of them were genuinely problematic or if our program is at fault.
Correct errors include \todo{find a real problem and describe shortly}.
Our program detected tagset errors also in the Finnish grammar.
The grammar was originally written in 1995, and converted to the Omorfi tagset by \cite{pirinen2015}. 
For example, the Omorfi tagset marks a possessive suffix with \texttt{Px}, e.g. \texttt{PxPl2} for second person plural, but the grammar used the old convention \texttt{PL2} in the rules.
As a result, all rules with possessive suffixes were detected as impossible.

Since we got our tagset from Omorfi, there was no ,
We suspect that at least part of the result is related to the length of the sentences---for a condition that states $n$ or more words to the left or right, we only create a word exactly $n$ words away. This is something to be fixed in the future.

The speed of the check is an obvious issue currently.
For Finnish and Spanish, each symbolic word has around 2500 variables in the beginning.
These variables represent tag combinations that come from the Apertium morphological lexicon. 
The Spanish lexicon includes up to two clitics (e.g. \emph{dámelo}, give.me.it) in the same word form, but none for Dutch but we excluded clitics for the Finnish tag combinations.
All morphological lexicons are from Apertium.

>>>>

The Spanish grammar had an erroneous set definition, where a word was required to have almost all POS tags at the same time. After fixing the set definition, our test didn't reveal other problems.
The program marked \todo{n} problem rules for the Finnish grammar, but we didn't have time to verify if all of them were genuinely problematic or if our program is at fault.
Correct errors include \todo{find a real problem and describe shortly}.
Our program detected tagset errors also in the Finnish grammar.
The grammar was originally written in 1995, and converted to the Omorfi tagset by \cite{pirinen2015}. 
For example, the Omorfi tagset marks a possessive suffix with \texttt{Px}, e.g. \texttt{PxPl2} for second person plural, but the grammar used the old convention \texttt{PL2} in the rules.
As a result, all rules with possessive suffixes were detected as impossible.
We suspect that at least part of the result is related to the length of the sentences---for a condition that states $n$ or more words to the left or right, we only create a word exactly $n$ words away. This is something to be fixed in the future.

The speed of the check is an obvious issue currently.
The Finnish symbolic word has around 5700 variables in the beginning of the analysis, each representing a possible tag combination.
Around 3700 come from the Apertium morphological lexicon, excluding clitics, and around 2000 are present in the grammar
For Spanish and Dutch, the numbers are around 2000 and 200 respectively.

These variables represent tag combinations that come from the Apertium morphological lexicon. 
The Spanish lexicon includes up to two clitics (e.g. \emph{dámelo}, give.me.it) in the same word form, but none for Dutch but we excluded clitics for the Finnish tag combinations.
All morphological lexicons are from Apertium.
